Using spatially biased variables in ecosystem condition accounting with a GIS based workflow

### 2024-02-01 manuscript/HIAs.qmd
something with the table

| id  | Variable code        | Variable name                                    | Measurement unit                                                                        | Description                                                                                                                                                        | Reference                          |
|--|--------------|--------------|--------------|--------------|--------------|
| 1   | 7FK                  | Prevalence of alien species                      | Unitless, ordinal, non-linear scale from 1 (no alien species) to 7 (only alien species) | The fraction of the species composition made up from alien species                                                                                                 | @runehalvorsen2019                 |
| 2   | 7SE                  | Human caused abration or abration-caused erosion | Unitless, ordinal, non-linear scale from 1 to 4.                                        | Measures the frequency of imagined 4 m^2^ quadrats layed over the area that has some sign of abration                                                              | @runehalvorsen2019                 |
| 3   | PRSL                 | *as above*                                       | Unitless, ordinal, non-linear scale from 0 to 7.                                        | Same as 7SE, but recorded at a higher resolution                                                                                                                   | @miljødirektoratet                 |
| 4   | 7TK                  | Tracks from large vehicles                       | Unitless, ordinal, non-linear scale from 1 to 4.                                        | Measures the frequency of imagined 100 m^2^ quadrats layed over the area that has some signs of vehicle tracks                                                     | @rune_halvorsen_dokumentasjon_2019 |
| 5   | PRTK                 | *as above*                                       | Unitless, ordinal, non-linear scale from 0 to 7.                                        | Same as 7TK, but recorded at a higher resolution                                                                                                                   | @miljødirektoratet                 |
| 6   | 7GR-GI               | Ditching intensity                               | Unitless, ordinal scale from 1 to 5                                                     | Describes the effect that drainage ditches is estimate to have on the species composition and environmental variables ones the system reached its new equilibrium  | @miljødirektoratet                 |
| 7   | Infrastructure Index | Infrastructure Index                             | Unitelss linear scale from 0 to 13.2                                                    | Unitelss index ranging from from 0 to 13.2                                                                                                                         | @erikstad_index_2023               |
| 8   | HIA                  | Human Impact area                                | Ordinal, non-linear scale from 1 to 4                                                   | A categorical representation of the infrastructure index                                                                                                           | this paper                         |

@@

| Municipality | Total terrestrial area (km^2^)                                            | \% of terrestrial area surveyed                                            | \% open mires in relation to total terrestrial area                         | Total mire area (km^2^)                                                  | %of mire area inside survey area                                                      | Number of mire polygons in survey                                 | Mean Infrastructure Index value                                         |
|---------|---------|---------|---------|---------|---------|---------|---------|
| Nordre Follo | `r muni_tbl |> filter(Municipality == "Nordre Follo") |> pull(t_area_km)` | `r muni_tbl |> filter(Municipality == "Nordre Follo") |> pull(dk_percent)` | `r muni_tbl |> filter(Municipality == "Nordre Follo") |> pull(mirePercent)` | `r muni_tbl |> filter(Municipality == "Nordre Follo") |> pull(mire_km2)` | `r muni_tbl |> filter(Municipality == "Nordre Follo") |> pull(mireInSurvery_percent)` | `r muni_tbl |> filter(Municipality == "Nordre Follo") |> pull(n)` | `r muni_tbl |> filter(Municipality == "Nordre Follo") |> pull(meanHIA)` |
| Trondheim    | `r muni_tbl |> filter(Municipality == "Trondheim") |> pull(t_area_km)`    | `r muni_tbl |> filter(Municipality == "Trondheim") |> pull(dk_percent)`    |                                                                             |                                                                          |                                                                                       | `r muni_tbl |> filter(Municipality == "Trondheim") |> pull(n)`    | `r muni_tbl |> filter(Municipality == "Trondheim") |> pull(meanHIA)`    |
| Målselv      | `r muni_tbl |> filter(Municipality == "Målselv") |> pull(t_area_km)`      | `r muni_tbl |> filter(Municipality == "Målselv") |> pull(dk_percent)`      |                                                                             |                                                                          |                                                                                       | `r muni_tbl |> filter(Municipality == "Målselv") |> pull(n)`      | `r muni_tbl |> filter(Municipality == "Målselv") |> pull(meanHIA)`      |

>>>>

| id  | Variable code        | Variable name                                    | Measurement unit                                                                        | Description                                                                                                                                                       | Reference                          |
|-----|----------------------|--------------------------------------------------|-----------------------------------------------------------------------------------------|-------------------------------------------------------------------------------------------------------------------------------------------------------------------|------------------------------------|
| 1   | 7FK                  | Prevalence of alien species                      | Unitless, ordinal, non-linear scale from 1 (no alien species) to 7 (only alien species) | The fraction of the species composition made up from alien species                                                                                                | @runehalvorsen2019                 |
| 2   | 7SE                  | Human caused abration or abration-caused erosion | Unitless, ordinal, non-linear scale from 1 to 4.                                        | Measures the frequency of imagined 4 m^2^ quadrats layed over the area that has some sign of abration                                                             | @runehalvorsen2019                 |
| 3   | PRSL                 | *as above*                                       | Unitless, ordinal, non-linear scale from 0 to 7.                                        | Same as 7SE, but recorded at a higher resolution                                                                                                                  | @miljødirektoratet                 |
| 4   | 7TK                  | Tracks from large vehicles                       | Unitless, ordinal, non-linear scale from 1 to 4.                                        | Measures the frequency of imagined 100 m^2^ quadrats layed over the area that has some signs of vehicle tracks                                                    | @rune_halvorsen_dokumentasjon_2019 |
| 5   | PRTK                 | *as above*                                       | Unitless, ordinal, non-linear scale from 0 to 7.                                        | Same as 7TK, but recorded at a higher resolution                                                                                                                  | @miljødirektoratet                 |
| 6   | 7GR-GI               | Ditching intensity                               | Unitless, ordinal scale from 1 to 5                                                     | Describes the effect that drainage ditches is estimate to have on the species composition and environmental variables ones the system reached its new equilibrium | @miljødirektoratet                 |
| 7   | Infrastructure Index | Infrastructure Index                             | Unitelss linear scale from 0 to 13.2                                                    | Unitelss index ranging from from 0 to 13.2                                                                                                                        | @erikstad_index_2023               |
| 8   | HIA                  | Human Impact area                                | Ordinal, non-linear scale from 1 to 4                                                   | A categorical representation of the infrastructure index                                                                                                          | this paper                         |

@@

| Municipality | Total terrestrial area (km^2^)                                            | \% of terrestrial area surveyed                                            | \% open mires in relation to total terrestrial area                         | Total mire area (km^2^)                                                  | %of mire area inside survey area                                                      | Number of mire polygons in survey                                 | Mean Infrastructure Index value                                         |
|--------------|---------------------------------------------------------------------------|----------------------------------------------------------------------------|-----------------------------------------------------------------------------|--------------------------------------------------------------------------|---------------------------------------------------------------------------------------|-------------------------------------------------------------------|-------------------------------------------------------------------------|
| Nordre Follo | `r muni_tbl |> filter(Municipality == "Nordre Follo") |> pull(t_area_km)` | `r muni_tbl |> filter(Municipality == "Nordre Follo") |> pull(dk_percent)` | `r muni_tbl |> filter(Municipality == "Nordre Follo") |> pull(mirePercent)` | `r muni_tbl |> filter(Municipality == "Nordre Follo") |> pull(mire_km2)` | `r muni_tbl |> filter(Municipality == "Nordre Follo") |> pull(mireInSurvery_percent)` | `r muni_tbl |> filter(Municipality == "Nordre Follo") |> pull(n)` | `r muni_tbl |> filter(Municipality == "Nordre Follo") |> pull(meanHIA)` |
| Trondheim    | `r muni_tbl |> filter(Municipality == "Trondheim") |> pull(t_area_km)`    | `r muni_tbl |> filter(Municipality == "Trondheim") |> pull(dk_percent)`    |                                                                             |                                                                          |                                                                                       | `r muni_tbl |> filter(Municipality == "Trondheim") |> pull(n)`    | `r muni_tbl |> filter(Municipality == "Trondheim") |> pull(meanHIA)`    |
| Målselv      | `r muni_tbl |> filter(Municipality == "Målselv") |> pull(t_area_km)`      | `r muni_tbl |> filter(Municipality == "Målselv") |> pull(dk_percent)`      |                                                                             |                                                                          |                                                                                       | `r muni_tbl |> filter(Municipality == "Målselv") |> pull(n)`      | `r muni_tbl |> filter(Municipality == "Målselv") |> pull(meanHIA)`      |
